Calculating life expectancy and exploring missingness

### 2016-10-26 Code/1_Explore_Data_v2.Rmd
prepping for cod graph

```{r calculate_cod_decomp}
#started at 12:01pm - guessing it will take 20 mins
list.cod.decomp.tables <- vector(mode = "list", length = dim(paired.ids)[1])

@@

    list.cod.decomp.tables[[i]] <- cause_of_death_decomp(life.table1 = as.data.frame(list.life.tables[[black.index]]),
                                                         life.table2 = as.data.frame(list.life.tables[[white.index]]), 
                                                         decomp.table = as.data.frame(list.age.decomp.tables[[i]]),
                                                         cod.table = ct.both, 
                                                         age.colname.cod.table = "Age2", 
                                                         COD.colname.cod.table = "COD2", 
                                                         prop1.colname.cod.table = "prop.black", 
                                                         prop2.colname.cod.table = "prop.white")
  } else {
    list.cod.decomp.tables[[i]] <- "Couldn't compare life tables"
  }  
  print(i)
}

i <- 1
white.index <- which(non.zero.stratums == paired.ids[i, "StateYearRaceSexWhite"])
black.index <- which(non.zero.stratums == paired.ids[i, "StateYearRaceSexBlack"])

    ct.white <- subset(dat.clean, StateYearRaceSex == paired.ids[i, "StateYearRaceSexWhite"]) %>% 
                ungroup() %>%
                select(Age2, COD2, cod_prop_death5) %>%
                rename(prop.white = cod_prop_death5)

    ct.black <- subset(dat.clean, StateYearRaceSex == paired.ids[i, "StateYearRaceSexBlack"]) %>% 
                ungroup() %>%
                select(Age2, COD2, cod_prop_death5) %>%
                rename(prop.black = cod_prop_death5)
    ct.both <- merge(ct.white, ct.black, by = c("Age2", "COD2")) 
    ct.both <- ct.both %>% arrange(COD2, Age2)
    View(ct.both)

test1 <- cause_of_death_decomp(life.table1 = as.data.frame(list.life.tables[[black.index]]),
                               life.table2 = as.data.frame(list.life.tables[[white.index]]), 
                               decomp.table = as.data.frame(list.age.decomp.tables[[i]]),
                               cod.table = ct.both, 
                               age.colname.cod.table = "Age2", 
                               COD.colname.cod.table = "COD2", 
                               prop1.colname.cod.table = "prop.black", 
                               prop2.colname.cod.table = "prop.white")

age_contr1 <- test1 %>% ungroup() %>% group_by(Ages) %>% summarise(age_contribution = sum(C_xi))
age_contr1
list.age.decomp.tables[[i]]
```

>>>>

```{r calculate_cod_decomp}
#takes about 20 mins
list.cod.decomp.tables <- vector(mode = "list", length = dim(paired.ids)[1])

@@

    list.cod.decomp.tables[[i]] <- cause_of_death_decomp(life.table1 = as.data.frame(list.life.tables[[black.index]]),
                                                         life.table2 = as.data.frame(list.life.tables[[white.index]]), 
                                                         decomp.table = as.data.frame(list.age.decomp.tables[[i]]),
                                                         cod.table = ct.both, 
                                                         age.colname.cod.table = "Age2", 
                                                         COD.colname.cod.table = "COD2", 
                                                         prop1.colname.cod.table = "prop.black", 
                                                         prop2.colname.cod.table = "prop.white")
  } else {
    list.cod.decomp.tables[[i]] <- "Couldn't compare life tables"
  }  
  print(i)
}
```

```{r}
first <- list.cod.decomp.tables[[1]]
first$sign <- ifelse(first$C_xi < 0, "negative", "positive")
first$group <- interaction(first$Ages, first$sign, sep = ".")

first <- first %>% 
  arrange(Ages, sign, Cause.of.death) %>%
  group_by(group) %>%
  mutate(lag = lag(C_xi), one = 1, 
         num = cumsum(one),
         length = n(),
         start = ifelse(is.na(lag)==T, 0, NA),
         finish = ifelse(is.na(lag)==T, C_xi, NA))
View(first)

updated <- NULL
for (g in unique(first$group)) {
  subset <- first[first$group == g, ]

  if(dim(subset)[1] > 1){
      for (i in 2:dim(subset)[1]) {
        subset$start[i] <- subset$finish[i - 1]
        subset$finish[i] <- subset$start[i] + subset$C_xi[i]
      }
  }

  updated <- rbind(updated, subset)
}
updated 
```
